Efficient Coalition Formation for Web Services

### 2013-03-12 papers/coalition/coalition.tex
Changes

The valuation function $v(C)$ for this scenario is same as \emph{one grand community} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.

@@

>>>>

@@

The valuation function $v(C)$ for this scenario is same as \emph{``Web Services and A Grand Community''} scenario, however in order to prevent master web services joining same community we set $v(C) = 0$, where C has none, or, two or more master web services as members.
